A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-03-21 sections/model_overview/main.tex
Apply reiview suggestions from Vince
Add diagram of the game (#36)
* Create a tikz image of the game

* Add minor changes to the text

* Update known words

* Remove the word "very"

* Fix caption

* Apply suggestions from Vince's review

Co-authored-by: Vince Knight <vince@vknight.org>

Co-authored-by: Vince Knight <vince@vknight.org>

The strategies of the two EDs are the range of thresholds that they can choose
from and their utilities is the proportion of individuals whose time in the 
system is within a predetermined target time.
The EMS has to decide how to distribute its patients among the two EDs so that 
the weighted combination of the ambulance blocking time and the percentage of 
lost ambulances is minimised. 
As defined in section \ref{sec:model_overview}, the interaction between the two
EDs is a normal form game that is then used to inform the decision of the EMS.
Note that the formulated game here assumes that prior to making a choice the 
EMS knows the strategies that each ED is playing (figure 
\ref{fig:imperfect_info_game}). 
This corresponds to reacting to experienced delays.

@@

Both hospitals follow a queueing model with two waiting spaces for 
individuals. 
The first waiting space (i.e. the waiting space of the hospital) is where the 
patients queue right before receiving 
their service and has a queue capacity of \( N - C \), where \(N\) is the total 
capacity of the hospital and \(C\) is the number of healthcare 
professionals able to see them.
% TODO: Should this be healthcare professionals or available beds?
The second waiting space (i.e. the parking space for ambulances) is where 
ambulances, that are sent from the
ambulance service, stay until their patients are allowed to enter the hospital.
The parking space has a capacity of \(M\) and no servers.

This is shown diagrammatically in Figure ~\ref{fig:diagram_of_queueing_system}.

% TODO: Add figure here of the game as described by issue #32

>>>>

The strategies of the two EDs are the range of thresholds that they can choose
from and their utilities is the proportion of individuals whose time in the 
system is within a predetermined target time.
The EMS has to decide how to distribute its patients among the two EDs so that 
the weighted combination of the ambulance blocking time and the percentage of 
lost ambulances is minimised. 
This can be illustrated by figure \ref{fig:diagram_of_game_theoretic_model}.
The interaction between the two
EDs is a normal form game that is then used to inform the decision of the EMS.
Note that the formulated game here assumes that prior to making a choice the 
EMS knows the strategies that each ED is playing (figure 
\ref{fig:imperfect_info_game}). 
This corresponds to reacting to experienced delays.

\input{imgs/game_theoretic_model_diagram/main.tex}

@@

Both hospitals follow a queueing model with two waiting spaces for 
individuals. 
The first waiting space (i.e. the waiting space of the hospital) is where the 
patients queue right before receiving 
their service and has a queue capacity of \( N - C \), where \(N\) is the total 
capacity of the hospital and \(C\) is the number of healthcare 
professionals able to see them.
% TODO: Should this be healthcare professionals or available beds?
The second waiting space (i.e. the parking space for ambulances) is where 
ambulances, that are sent from the
ambulance service, stay until their patients are allowed to enter the hospital.
The parking space has a capacity of \(M\) and no servers.
This is shown diagrammatically in Figure~\ref{fig:diagram_of_queueing_system}.
